### 2014-11-13 tex/evaluation.tex
Added a short summary to the evaluation.

>>>>

In summary, it appears that the benefits of avoiding initialization-based nondeterminism more than outweigh the increased complexity in the constraints. In fact, \symtxt{} can analyze certain types of programs with orders of magnitude greater efficiency than with \gsetxt{} or lazier#, while covering exactly the same test cases with zero loss of precision.
